---
title: "P8105_Homework 1"
author: "Linh Tran"
date: "9/14/2020"
output: github_document
---

This is my solution to HW1. 

```{r setup, include = FALSE}
library(tidyverse)
```

## Prolem 1

The chunk below creates a data frame comprised of variables.

```{r create_df}
prob1_df =  tibble (
             samp = rnorm (10),
             vec_logical = samp > 0,
             vec_char = c ("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
             vec_factor = factor (c("yes", "maybe", "no", "yes", "no", "maybe", "yes", "no", "maybe", "yes"))
)
```

Take the mean of each variable in my data frame.

```{r mean_pull_var, eval = FALSE}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, vec_logical))
mean(pull(prob1_df, vec_char))
mean(pull(prob1_df, vec_factor))
```

I can take the mean of numbers and logical but not character or factor.

The chunk below converts variables to numeric and multiplys the random sample by the result
```{r converting_numeric, eval = FALSE}
as.numeric (pull(prob1_df, samp))
as.numeric (pull(prob1_df, vec_logical))
as.numeric (pull(prob1_df, vec_char))
as.numeric (pull(prob1_df, vec_factor))

as.numeric (pull(prob1_df, vec_logical)) * pull (prob1_df, samp)
as.factor (pull(prob1_df, vec_logical)) * pull (prob1_df, samp)
as.numeric (as.factor (pull(prob1_df, vec_logical))) * pull (prob1_df, samp)
```
This is the end of Problem 1. 

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

* Some descriptions of the penguins dataset:
    + The categories of the variables in the dataset is `r names(penguins)`.
    + The species of the penguins in the dataset are `r levels(penguins$species)`, and they live on `r levels (penguins$island)` islands. 
    + The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
    + The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.




